\subsection{Scope}
This document shows how the acceptance testing is performed on an implementation of CLup done by another group.

The acceptance testing performed on prototype is driven by the specifications, the design decisions and the implementation provided from the team 
in written form on the \textbf{RASD}, \textbf{DD}, and \textbf{ITD}.

The implementation on which this acceptance this acceptance test is perfomerd is the one made by Nicolò Sonnino 
and Luca Pirovano and could be found at \href{https://github.com/PiroX4256/SE2-Piemonti-Pirovano-Sonnino}{this Github repository}.

\subsection{Document Structure}

\textbf{Chapter 1} explains the purpose of this document.
Acronyms and Definitions used through the whole document are listed and explained.
It provides the history of the document revisions and this very description of all the chapters, together with the documents used as a reference.

\medskip

\textbf{Chapter 2} shows how the installation was performed, following the documentation provided in the \textbf{ITD}.

\medskip

\textbf{Chapter 3} shows all the acceptance test cases performed with their outcome. For each issue a complete bug report is provided.

\medskip


\textbf{Chapter 4} contains the conclusions of this Acceptance test.

\medskip

\textbf{Chapter 5} shows the time spent from each member of the team for writing this document.

\clearpage
\subsection{Definitions, Acronyms, Abbreviations}

\subsubsection{Acronyms}

\begin{itemize}
    \item \textbf{S2B}: Software To Be
    \item \textbf{RASD}: Requirement Analysis and Specifications Documents
    \item \textbf{REST}: REpresentational State Transfer
    \item \textbf{API}: Application Programming Interface
    \item \textbf{UX}: User Experience
    \item \textbf{UI}: User Interface
    \item \textbf{SSO}: Single sign-on
    \item \textbf{QR code}: Quick Response code
    \item \textbf{OS}: Operating System
    \item \textbf{RAM}: Random Access Memory
    \item \textbf{LAN}: Local Area Network
    \item \textbf{GPS}: Global Positioning System
    \item \textbf{GB}: GigaByte
    \item \textbf{TCP/IP}: Transmission Control Protocol/Internet Protocol
    \item \textbf{HTTPS}: Hypertext Transfer Protocol Secure
    \item \textbf{IoT}: Internet of Things
    \item \textbf{MQTT}: Message Queuing Telemetry Transport
    \item \textbf{RAID}: Redundant Array of Independent Disks
    \item \textbf{UML}: Unified Modeling Language
    \item \textbf{TDD}: Test-driven development
    \item \textbf{WSGI}: Web Server Gateway Interface
    \item \textbf{ATD}: Acceptance Testing Document
\end{itemize}

\vfill
\pagebreak

\subsubsection{Definitions}

\begin{itemize}
    \item \textbf{Access controller}: a subsystem that permits the entrance of customers into the store. It can be a device like a smart turnstile that reads customers tickets or just a person of the store staff manually scanning tickets.
    \item \textbf{Business account}: a CLup account that is destined to store managers or operators and therefore the 'business' side of CLup
    \item \textbf{In-Site ticket}: a ticket that is taken by a customer near the store. It can be both a virtual paperless ti an emitter near the store premises
    \item \textbf{Virtual ticket}: a ticket issued through the CLup application
    \item \textbf{Physical/Paper ticket}: a printed physical ticket, emitted by a printer near the store premises
    \item \textbf{Valid Ticket} (at time X): a ticket that has a code recognized by the CLup system and valid for the specified time
    \item \textbf{Time slot}: a time delta that is associated with a number of bookable tickets (which varies and is customizable from store to store)
    \item \textbf{People-Counting System}: a subsystem that permits the counting of the number of people inside the store. It can comprehend a device like a proximity sensor or a smart turnstile, or it can be a person of the store staff manually counting people.
    \item \textbf{Customer Application}: the CLup mobile application destined to customers that want to shop inside stores adopting CLup
    \item \textbf{Operator Application}: the CLup mobile application destined to store staff to monitor entrances and statistics
    \item \textbf{Store Main System}: the store main server that communicates directly with CLup servers. All store subsystems and smart devices should communicate with it through an Intranet
    \item \textbf{Geocoding API}: Geocoding converts addresses into geographic coordinates to be placed on a map. A Geocoding API allows the use of their services to permit translation between textual addresses and Latitude/Longitude coordinates
    \item \textbf{Map API}: An external services that provides operations of geographics maps and the download of map information, usually of the places in proximity of given geographics coordinates
    \item \textbf{Hashed Password}: When a password has been “hashed” it means it has been turned into a scrambled representation of itself. A user's password is taken and – using a key known to the site – the hash value is derived from the combination of both the password and the key, using a set algorithm.
    \item \textbf{Time to market}: is the length of time it takes from a product being conceived until its being available for sale.
    \item \textbf{Alpha Test}: a trial of machinery, software, or other products carried out by a developer before a product is made available for beta testing.
    \item \textbf{Beta Test}: a trial of machinery, software or other products in the final stages of development, carried out by a party unconnected with the development process.
    \item \textbf{DevOps}: is a set of practices that combines software development (Dev) and IT operations (Ops). It aims to shorten the systems development life cycle and provide continuous delivery with high software quality.
    \item \textbf{Quality Assessment}: is the data collection and analysis through which the degree of conformity to predetermined standards and criteria are exemplified.
\end{itemize}

\subsection{Revision History}

\begin{itemize}
    \item 1.0: 14 January 2021 - First Release
\end{itemize}

\subsection{Reference Documents}

\begin{itemize}
    \item R\&DD Assignment A.Y. 2020-2021 - Elisabetta di Nitto, Matteo Giovanni Rossi
    \item Software Engineering II slides and material - Elisabetta di Nitto, Matteo Giovanni Rossi
    \item CLup RASD - Nicolò Sonnino, Luca Pirovano
    \item CLup DD - Nicolò Sonnino, Luca Pirovano
    \item CLup ITD - Nicolò Sonnino, Luca Pirovano
    \item \href{https://material.io/design}{Material Design Guidelines}
    \item \href{https://www.conventionalcommits.org/en/v1.0.0/}{Convetional Commits Guidelines}
    \item \href{https://git-scm.com/}{Git - versioning system}
\end{itemize}

\subsection{Used Tools}
\begin{itemize}
    \item Github - for code hosting and version control
    \item \LaTeX \space  - to write this entire document
    \item Visual Studio Code + Latex Workshop - as a \LaTeX \space environment
\end{itemize}

\subsection{Team Contacts}
\begin{itemize}
    \item Dario Passarello: dario.passarello@mail.polimi.it
    \item Davide Merli: davideluca.merli@mail.polimi.it
\end{itemize}

\clearpage